---
title: "NeuralNetwork"
output:
  html_document: default
  pdf_document: default
---

```{r }

#install.packages("neuralnet")

```

# Create a dataset, Technical Knowledge Score (TKK) and Communication Skills Score (CSS) as features, and "placed" as a class label

```{r}

# creating training data set
TKS=c(20,10,30,20,80,30)
CSS=c(90,20,40,50,50,80)
Placed=c(1,0,0,0,1,1)

# Here, you will combine multiple columns or features into a single set of data
df=data.frame(TKS,CSS,Placed)

```

# Let's build a NN classifier model using the neuralnet library.
# First, import the neuralnet library and create NN classifier model by passing argument set of label and features, dataset, number of neurons in hidden layers, and error calculation.

# - Placed~TKS+CSS, Placed is label annd TKS and CSS are features.
#  - df is dataframe,
#  - hidden=3: represents single layer with 3 neurons respectively.
#  - act.fct = "logistic" used for smoothing the result.
#  - linear.ouput=FALSE: set FALSE for apply act.fct otherwise TRUE

```{r}

require(neuralnet)
# fit neural network
nn=neuralnet(Placed~TKS+CSS,data=df, hidden=3,act.fct = "logistic",
                linear.output = FALSE)

```


## Plotting Neural Network
#     Let's plot your neural net model.Including Plots


```{r}
# plot neural network
plot(nn)

```

# Create test dataset using two features Technical Knowledge Score (TKK) and Communication Skills Score (CSS)

```{r pressure, echo=FALSE}

 TKS=c(30,40,85)
CSS=c(85,50,40)
test=data.frame(TKS,CSS)

```

# Predict the results for the test set
# Predict the probability score for the test data using the compute function.



```{r}
## Prediction using neural network
Predict=compute(nn,test)
Predict$net.result

```

# # Converting probabilities into binary classes setting threshold level 0.5


```{r}
prob <- Predict$net.result
pred <- ifelse(prob>0.5, 1, 0)
pred

```

#Predicted results are 1,0, and 1.

#<b> Pros and Cons </b>
#Neural networks are more flexible and can be used with both regression and classification problems. Neural networks are #good for the nonlinear dataset with a large number of inputs such as images. Neural networks can work with any number of #inputs and layers. Neural networks have the numerical strength that can perform jobs in parallel.

#There are more alternative algorithms such as SVM, Decision Tree and Regression are available that are simple, fast, #easy to train, and provide better performance. Neural networks are much more of the black box, require more time for #development and more computation power. Neural Networks requires more data than other Machine Learning algorithms. NNs #can be used only with numerical inputs and non-missing value datasets. A well-known neural network researcher said "A #neural network is the second best way to solve any problem. The best way is to actually understand the problem,"

#<b> Use-cases of NN </b>

#NN's wonderful properties offer many applications such as:

#Pattern Recognition: neural networks are very suitable for pattern recognition problems such as facial recognition, #object detection, fingerprint recognition, etc.
#Anomaly Detection: neural networks are good at pattern detection, and they can easily detect the unusual patterns that #don’t fit in the general patterns.
#Time Series Prediction: Neural networks can be used to predict time series problems such as stock price, weather #forecasting.
#Natural Language Processing: Neural networks offer a wide range of applications in Natural Language Processing tasks #such as text classification, Named Entity Recognition (NER), Part-of-Speech Tagging, Speech Recognition, and Spell #Checking.

#Conclusion
#Congratulations, you have made it to the end of this tutorial!

#In this tutorial, you have covered a lot of details about the Neural Network. You have learned what Neural Network, #Forward Propagation, and Back Propagation are, along with Activation Functions, Implementation of the neural network in #R, Use-cases of NN, and finally Pros, and Cons of NN.

#Hopefully, you can now utilize Neural Network concept to analyze your own datasets. Thanks for reading this tutorial/!